### 2023-12-16 thesis/chapters/03-design.tex
Activity diagram of data preparation

\section{Research questions}
This thesis aims to provide answers to four broader formulated research questions. The focus is primarily on making data flow more efficient in an industrial sensor network that monitors rotating machines. The \textbf{research questions} are:
\begin{enumerate}
    \itemsep0pt
	\item Which temporal and spectral features can be extracted from vibration signals to provide the most accurate record of machinery faults?
	\item What is the reduction in transmission goodput when chosen signal features are used?
	\item What accuracies of prediction models can be achieved with various feature subsets? 
	\item How can machinery faults be continuously identified and predicted based upon collected events?
\end{enumerate}

@@

\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{0.44\textwidth}
        \includegraphics[width=\textwidth]{assets/design/Mafaulda-A-time-waveform.png}
        \caption{Temporal domain waveforms in all spatial directions with 300 ms duration}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.55\textwidth}
        \includegraphics[width=\textwidth]{assets/design/Mafaulda-A-spectrum-Y-axis.png}
        \caption{Spectral domain in radial direction (y). FFT with Hann window of length $2^{14}$ ($\approx 328$ ms)}
    \end{subfigure} 
    \caption{Signals at 1 s timestamp from inner bearing in each fault category with the highest fault severity}
\end{figure}

\section{Dataset preparation}

@@

\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{\textwidth}
        \includegraphics[width=\textwidth]{assets/design/pca-scatter-online-fault-temporal.png}
        \caption{}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{\textwidth}
        \includegraphics[width=\textwidth]{assets/design/pca-scatter-online-fault-spectral.png}
        \caption{}
    \end{subfigure}
    \begin{subfigure}[b]{\textwidth}
        \includegraphics[width=\textwidth]{assets/design/pca-scatter-online-anomaly60-temporal.png}
        \caption{}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{\textwidth}
        \includegraphics[width=\textwidth]{assets/design/pca-scatter-online-anomaly60-spectral.png}
        \caption{}
    \end{subfigure}
    \caption{PCA 2 components to visualize results and mistakes of online learning on all features}
\end{figure}
)

>>>>

\section{Research questions}
This thesis aims to provide answers to four research questions formulated in broader sense. The focus is primarily on making data flow more efficient in an industrial sensor network that monitors rotating machines. The \textbf{research questions} are:
\begin{enumerate}[label=RQ\arabic*., font=\bfseries]
    \itemsep0pt
	\item Which temporal and spectral features can be extracted from vibration signals to provide the most accurate record of machinery faults?
	\item What is the reduction in transmission goodput when chosen signal features are used?
	\item What accuracies of prediction models can be achieved with various feature subsets?
	\item How can machinery faults be continuously identified and predicted based upon collected events?
\end{enumerate}

@@

\section{Dataset exploration}

\begin{figure}[ht]
	\centering
	\includegraphics[width=\textwidth]{assets/design/activity-data-exploration.png}
	\caption{Activity diagram of MaFaulDa dataset preprocessing}
\end{figure}

\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{0.44\textwidth}
        \includegraphics[width=\textwidth]{assets/design/Mafaulda-A-time-waveform.png}
        \caption{Temporal domain waveforms in all spatial directions with 300 ms duration}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.55\textwidth}
        \includegraphics[width=\textwidth]{assets/design/Mafaulda-A-spectrum-Y-axis.png}
        \caption{Frequency spectrum in radial direction (y)}
    \end{subfigure} 
    \caption{Signals at 1 s timestamp from inner bearing in each fault category with the highest fault severity}
\end{figure}

\begin{table}[ht]
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{rrrrrllll}
\cline{1-5}
\multicolumn{1}{|l|}{\multirow{2}{*}{\textbf{Fault}}} & \multicolumn{2}{l|}{\textbf{All rotational speeds}}                                               & \multicolumn{2}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Selected rotational speeds \\ 2500 $\pm$ 500 rpm\end{tabular}}} &                               &                               &                               &                               \\ \cline{2-5}
\multicolumn{1}{|l|}{}                                & \multicolumn{1}{l|}{\textbf{Inner bearing (A)}} & \multicolumn{1}{l|}{\textbf{Outer bearing (B)}} & \multicolumn{1}{l|}{\textbf{Inner bearing (A)}}            & \multicolumn{1}{l|}{\textbf{Outer bearing (B)}}           &                               &                               &                               &                               \\ \cline{1-5}
\multicolumn{1}{|r|}{\textbf{normal}}                 & \multicolumn{1}{r|}{49 (3\%)}                   & \multicolumn{1}{r|}{49 (4\%)}                   & \multicolumn{1}{r|}{16 (3\%)}                              & \multicolumn{1}{r|}{16 (3\%)}                             &                               &                               &                               &                               \\ \cline{1-5}
\multicolumn{1}{|r|}{\textbf{misalignment}}           & \multicolumn{1}{r|}{498 (35\%)}                 & \multicolumn{1}{r|}{498 (36\%)}                 & \multicolumn{1}{r|}{173 (34\%)}                            & \multicolumn{1}{r|}{173 (36\%)}                           &                               &                               &                               &                               \\ \cline{1-5}
\multicolumn{1}{|r|}{\textbf{imbalance}}              & \multicolumn{1}{r|}{333 (23\%)}                 & \multicolumn{1}{r|}{333 (24\%)}                 & \multicolumn{1}{r|}{118 (23\%)}                            & \multicolumn{1}{r|}{118 (25\%)}                           &                               &                               &                               &                               \\ \cline{1-5}
\multicolumn{1}{|r|}{\textbf{cage fault}}             & \multicolumn{1}{r|}{188 (13\%)}                 & \multicolumn{1}{r|}{188 (13\%)}                 & \multicolumn{1}{r|}{67 (13\%)}                             & \multicolumn{1}{r|}{69 (14\%)}                            &                               &                               &                               &                               \\ \cline{1-5}
\multicolumn{1}{|r|}{\textbf{ball fault}}             & \multicolumn{1}{r|}{186 (13\%)}                 & \multicolumn{1}{r|}{137 (10\%)}                 & \multicolumn{1}{r|}{61 (12\%)}                             & \multicolumn{1}{r|}{34 (7\%)}                             &                               &                               &                               &                               \\ \cline{1-5}
\multicolumn{1}{|r|}{\textbf{outer race fault}}       & \multicolumn{1}{r|}{184 (13\%)}                 & \multicolumn{1}{r|}{188 (13\%)}                 & \multicolumn{1}{r|}{69 (14\%)}                             & \multicolumn{1}{r|}{68 (14\%)}                            &                               &                               &                               &                               \\ \cline{1-5}
\multicolumn{1}{|r|}{\textbf{Total}}                  & \multicolumn{1}{r|}{1438}                       & \multicolumn{1}{r|}{1393}                       & \multicolumn{1}{r|}{504}                                   & \multicolumn{1}{r|}{478}                                  & \multicolumn{1}{r}{\textbf{}} & \multicolumn{1}{r}{\textbf{}} & \multicolumn{1}{r}{\textbf{}} & \multicolumn{1}{r}{\textbf{}} \\ \cline{1-5}
\textbf{}                                             &                                                 &                                                 &                                                            &                                                           & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          \\
\textbf{}                                             &                                                 &                                                 &                                                            &                                                           & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          \\
\textbf{}                                             &                                                 &                                                 &                                                            &                                                           & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          \\
\textbf{}                                             &                                                 &                                                 &                                                            &                                                           & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          \\
                                                      &                                                 &                                                 &                                                            &                                                           & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          \\
                                                      &                                                 &                                                 &                                                            &                                                           & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}         
\end{tabular}
\end{table}

\begin{table}[ht]
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{rrrrrrrrr}
\cline{1-5}
\multicolumn{1}{|l|}{\multirow{2}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}Anomaly\\ 60\% severity\end{tabular}}}} & \multicolumn{2}{l|}{\textbf{All rotational speeds}}                                               & \multicolumn{2}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Selected rotational speeds \\ 2500 $\pm$ 500 rpm\end{tabular}}} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\ \cline{2-5}
\multicolumn{1}{|l|}{}                                                                                          & \multicolumn{1}{l|}{\textbf{Inner bearing (A)}} & \multicolumn{1}{l|}{\textbf{Outer bearing (B)}} & \multicolumn{1}{l|}{\textbf{Inner bearing (A)}}            & \multicolumn{1}{l|}{\textbf{Outer bearing (B)}}           & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\ \cline{1-5}
\multicolumn{1}{|r|}{\textbf{False}}                                                                            & \multicolumn{1}{r|}{837 (58\%)}                 & \multicolumn{1}{r|}{831 (60\%)}                 & \multicolumn{1}{r|}{375 (74\%)}                            & \multicolumn{1}{r|}{354 (74\%)}                           & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\ \cline{1-5}
\multicolumn{1}{|r|}{\textbf{True}}                                                                             & \multicolumn{1}{r|}{601 (42\%)}                 & \multicolumn{1}{r|}{562 (40\%)}                 & \multicolumn{1}{r|}{129 (26\%)}                            & \multicolumn{1}{r|}{124 (26\%)}                           & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\ \cline{1-5}
\multicolumn{1}{|r|}{\textbf{Total}}                                                                                 & \multicolumn{1}{r|}{1438}                       & \multicolumn{1}{r|}{1393}                       & \multicolumn{1}{r|}{504}                                   & \multicolumn{1}{r|}{478}                                  & \textbf{}            & \textbf{}            & \textbf{}            & \textbf{}            \\ \cline{1-5}
\textbf{}                                                                                                       &                                                 &                                                 &                                                            &                                                           &                      &                      &                      &                      \\
\textbf{}                                                                                                       & \textbf{}                                       & \textbf{}                                       & \textbf{}                                                  & \textbf{}                                                 & \textbf{}            & \textbf{}            & \textbf{}            & \textbf{}            \\
\textbf{}                                                                                                       &                                                 &                                                 &                                                            &                                                           &                      &                      &                      &                      \\
\textbf{}                                                                                                       &                                                 &                                                 &                                                            &                                                           &                      &                      &                      &                      \\
                                                                                                                &                                                 &                                                 &                                                            &                                                           &                      &                      &                      &                      \\
                                                                                                                &                                                 &                                                 &                                                            &                                                           &                      &                      &                      &                     
\end{tabular}
\end{table}

\begin{table}[ht]
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{rrrrrrrrr}
\cline{1-5}
\multicolumn{1}{|l|}{\multirow{2}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}Anomaly\\ 90\% severity\end{tabular}}}} & \multicolumn{2}{l|}{\textbf{All rotational speeds}}                                               & \multicolumn{2}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Selected rotational speeds \\ 2500 $\pm$ 500 rpm\end{tabular}}} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\ \cline{2-5}
\multicolumn{1}{|l|}{}                                                                                          & \multicolumn{1}{l|}{\textbf{Inner bearing (A)}} & \multicolumn{1}{l|}{\textbf{Outer bearing (B)}} & \multicolumn{1}{l|}{\textbf{Inner bearing (A)}}            & \multicolumn{1}{l|}{\textbf{Outer bearing (B)}}           & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\ \cline{1-5}
\multicolumn{1}{|r|}{\textbf{False}}                                                                            & \multicolumn{1}{r|}{837 (58\%)}                 & \multicolumn{1}{r|}{831 (60\%)}                 & \multicolumn{1}{r|}{375 (74\%)}                            & \multicolumn{1}{r|}{354 (74\%)}                           & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\ \cline{1-5}
\multicolumn{1}{|r|}{\textbf{True}}                                                                             & \multicolumn{1}{r|}{601 (42\%)}                 & \multicolumn{1}{r|}{562 (40\%)}                 & \multicolumn{1}{r|}{129 (26\%)}                            & \multicolumn{1}{r|}{124 (26\%)}                           & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\ \cline{1-5}
\multicolumn{1}{|r|}{\textbf{Total}}                                                                                 & \multicolumn{1}{r|}{1438}                       & \multicolumn{1}{r|}{1393}                       & \multicolumn{1}{r|}{504}                                   & \multicolumn{1}{r|}{478}                                  & \textbf{}            & \textbf{}            & \textbf{}            & \textbf{}            \\ \cline{1-5}
\textbf{}                                                                                                       &                                                 &                                                 &                                                            &                                                           &                      &                      &                      &                      \\
\textbf{}                                                                                                       & \textbf{}                                       & \textbf{}                                       & \textbf{}                                                  & \textbf{}                                                 & \textbf{}            & \textbf{}            & \textbf{}            & \textbf{}            \\
\textbf{}                                                                                                       &                                                 &                                                 &                                                            &                                                           &                      &                      &                      &                      \\
\textbf{}                                                                                                       &                                                 &                                                 &                                                            &                                                           &                      &                      &                      &                      \\
                                                                                                                &                                                 &                                                 &                                                            &                                                           &                      &                      &                      &                      \\
                                                                                                                &                                                 &                                                 &                                                            &                                                           &                      &                      &                      &                     
\end{tabular}
\end{table}

@@

\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{\textwidth}
        \includegraphics[width=\textwidth]{assets/design/pca-scatter-online-fault-temporal.png}
        \caption{}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{\textwidth}
        \includegraphics[width=\textwidth]{assets/design/pca-scatter-online-fault-spectral.png}
        \caption{}
    \end{subfigure}
    \begin{subfigure}[b]{\textwidth}
        \includegraphics[width=\textwidth]{assets/design/pca-scatter-online-anomaly60-temporal.png}
        \caption{}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{\textwidth}
        \includegraphics[width=\textwidth]{assets/design/pca-scatter-online-anomaly60-spectral.png}
        \caption{}
    \end{subfigure}
    \caption{PCA 2 components to visualize results and mistakes of online learning on all features}
\end{figure}
